Hypotheses

### 2023-02-15 analysis/hypotheses.qmd
Adjust hypothesis count

We test three sets of hypotheses:

@@

## H~3~: Civil society, derogations, and pandemic-related economic policies

- **H~3a~**: If civil society organizations are involved in the policy making process and consulted by the government), then states are more likely to have supportive economic policies during the pandemic.
- **H~3b~**: If states formally derogate from their international treaty provisions, then states are more likely to have supportive economic policies during the pandemic.

>>>>

We test two sets of hypotheses:

@@
